Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
add an introduction to hydras

\subsection{Hydra games}
Hydra games (also known as \emph{Hydra battles}) appear in an article published in 1982 by two mathematicians, 
Laurie Kirby and Jeff Paris: \emph{Accessible Independence Results for Peano Arithmetic}~\cite{KP82}.
This article describes a game between two players: Hercules and a hydra.
A short description of the game  can be found in~\cite{bauer2008, KP82, JFLA2018paper}. One can also play with
Andrej Bauer's simulator~\cite{BauerHydra}.
In a few words:
\begin{itemize}
\item A hydra is a finite tree, traditionally presented with the root at the bottom, the leaves of which are called \emph{heads}
  (Fig~\ref{fig:round}).
\item At every round, Hercules chops off one head of the hydra. If the head is at a distance greater than 1 from the root,
  then some sub-tree $h$ of the hydra is copied a certain amount $n$ of times. The number $n$ of copies and the sub-tree $h$ may depend of the considered variant of the game
  or the time elapsed since the beginning of the fight.
  Figure~\ref{fig:round} shows an example with $n=2$.
\end{itemize}

>>>>

\subsection{Hydra games}

We chose to build our library and book on two simple themes which allow many variations: computing powers in a monoid, and Kirby and Paris' hydra battles, formerly user contributions of the Coq system. In the interest of space, we shall present only the second one in this article.

Hydra games (also known as \emph{Hydra battles}) appear in an article published in 1982 by two mathematicians, 
Laurie Kirby and Jeff Paris: \emph{Accessible Independence Results for Peano Arithmetic}~\cite{KP82}.
This article describes a game between two players: Hercules and a hydra.
A short description of the game  can be found in~\cite{bauer2008, KP82, JFLA2018paper}. One can also play with
Andrej Bauer's simulator~\cite{BauerHydra}.
In a few words:
\begin{itemize}
\item A hydra is a finite tree, traditionally presented with the root at the bottom, the leaves of which are called \emph{heads}
  (Fig~\ref{fig:round}).
\item At every round, Hercules chops off one head of the hydra. If the head is at a distance greater than 1 from the root,
  then some sub-tree $h$ of the hydra is copied a certain amount $n$ of times. The number $n$ of copies and the sub-tree $h$ may depend of the considered variant of the game
  or the time elapsed since the beginning of the fight.
  Figure~\ref{fig:round} shows an example with $n=2$.
\end{itemize}
